Music Recommendation System Using the Million Song Dataset

### 2015-05-08 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

\begin{table}[h]
\begin{center}
\begin{tabular}{lll}
\hline
Measurement & Plays Across Songs & Plays Across Users \\
\hline
Count &  163206 & 110000 \\
Mean  &     8.890194 & 13.190300  \\
Std      &    46.780258 & 8.070827 \\
Min      &    1.0  & 5.0  \\
Max     &   5043 &  53 \\
\end{tabular}
\caption{Basic summary statistics for the full data set.}
\label{tab:stats}
\end{center}
\end{table}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{../plots/final/cumsum-users.png} 
   \caption{Percentage of songs accounted for versus users with increasing number of plays.}
   \label{fig:t}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{lll}
\hline
Measurement & Plays Across Songs & Plays Across Users \\
\hline
Count &  163206 & 110000 \\
Mean  &     8.890194 & 13.190300  \\
Std      &    46.780258 & 8.070827 \\
Min      &    1.0  & 5.0  \\
Max     &   5043 &  53 \\
\end{tabular}
\caption{Basic summary statistics for the full data set.}\label{tab:stats}
\end{center}
\end{table}

It is also easy to see in the below chart that the majority of the songs are listened to by very few users so we can decrease the number of songs in our subset but not lose all of the play count.

@@

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=4in]{../plots/final/cumsum-users.png} 
%   \caption{Percentage of songs accounted for versus users with increasing number of plays.}
%   \label{fig:t}
%\end{figure}
